Effect of character correlation

### 2017-07-27 Analysis/EffectCorrelationStats.Rmd
Stats vignette

Getting the functions and the data

```{r, eval = TRUE, message = FALSE}
library(dispRity)
library(lme4)
library(lmerTest)
library(ordinal)
library(MASS)
source("functions.R") ; load.functions(test = FALSE)
dyn.load("../Functions/char.diff.so")
load("../Data/NTS/matrix.nts.Rda")
source("../Data/load.data.R")
```

@@

```{r}
## Getting the whole data
whole_data <- list("t25" = t25_list, "t75" = t75_list, "t150" = t150_list)

## getting the aov data
aov_data_RF_best <- get.aov.data(whole_data, "RF", "norm", combined = TRUE)
aov_data_Tr_best <- get.aov.data(whole_data, "Triples", "norm", combined = TRUE)
aov_data_RF_null <- get.aov.data(whole_data, "RF", "null", combined = TRUE)
aov_data_Tr_null <- get.aov.data(whole_data, "Triples", "null", combined = TRUE)

@@

All our models violate a least one of the two models assumptions (normality of the residuals and homoscedasticity of variance) and thus cannot be used to compare the scenarios.

@@

```{r}
## Running the pairwise Bhattacharrya Coefficient analysis:
(bc_RF_best <- run.bhatt.coeff(whole_data, "RF", "norm"))
(bc_Tr_best <- run.bhatt.coeff(whole_data, "Triples", "norm"))
(bc_RF_null <- run.bhatt.coeff(whole_data, "RF", "null"))
(bc_Tr_null <- run.bhatt.coeff(whole_data, "Triples", "null"))
```

Non-parametric anova
-----------------------------------

```{r}
# ## Cumulative Link Mixed Models
# mm1 <- clmm(NTS ~ scenario + (1|taxa/method) + (1|character/method),
#             data = aov_data_RF_best)
# mm1
# summary(mm1)

# ## Ordinated logistic regression
# polr(scenario ~ NTS + (1) ,
#                       data = aov_data_RF_best)

>>>>

Getting the functions and the data.

```{r, eval = TRUE, message = FALSE}
library(dispRity)
library(lme4)
library(lmerTest)
source("functions.R") ; load.functions(test = FALSE)
dyn.load("../Functions/char.diff.so")
load("../Data/NTS/matrix.nts.Rda")
source("../Data/load.data.R")

## Getting the whole data
whole_data <- list("t25" = t25_list, "t75" = t75_list, "t150" = t150_list)
```

Summary statistics
-----------------------------------

We can also apply a non-parametric pairwise comparison between scenarios for each parameters combinations.
Note however that the resulting p-values are not always exact due to ties in the results (again, due to the metric being bounded to 1).
The p-values are adjusted for multiple tests using Bonferroni-Holm correction.

```{r}
## Running the pairwise Wilcox tests:
(sum_RF_best <- apply.test(whole_data, "RF", "norm", NULL))
(sum_Tr_best <- apply.test(whole_data, "Triples", "norm", NULL))
(sum_RF_null <- apply.test(whole_data, "RF", "null", NULL))
(sum_Tr_null <- apply.test(whole_data, "Triples", "null", NULL))

@@

```{r}
## getting the aov data
aov_data_RF_best <- get.aov.data(whole_data, "RF", "norm", combined = TRUE)
aov_data_Tr_best <- get.aov.data(whole_data, "Triples", "norm", combined = TRUE)
aov_data_RF_null <- get.aov.data(whole_data, "RF", "null", combined = TRUE)
aov_data_Tr_null <- get.aov.data(whole_data, "Triples", "null", combined = TRUE)

@@

All our models violate a least one of the two models assumptions (normality of the residuals and homoscedasticity of variance) and thus cannot be used to compare the scenarios.
This is due to the fact that the metric is bounded to 1.

@@

```{r}
## Running the pairwise Bhattacharrya Coefficient analysis:
(bc_RF_best <- apply.test(whole_data, "RF", "norm", bhatt.coeff))
(bc_Tr_best <- apply.test(whole_data, "Triples", "norm", bhatt.coeff))
(bc_RF_null <- apply.test(whole_data, "RF", "null", bhatt.coeff))
(bc_Tr_null <- apply.test(whole_data, "Triples", "null", bhatt.coeff))
```

Non-parametric pairwise comparisons
-----------------------------------

We can also apply a non-parametric pairwise comparison between scenarios for each parameters combinations.
Note however that the resulting p-values are not always exact due to ties in the results (again, due to the metric being bounded to 1).
The p-values are adjusted for multiple tests using Bonferroni-Holm correction.

```{r}
## Running the pairwise Wilcox tests:
wx_RF_best <- apply.test(whole_data, "RF", "norm", wilcox.test)
wx_Tr_best <- apply.test(whole_data, "Triples", "norm", wilcox.test)
wx_RF_null <- apply.test(whole_data, "RF", "null", wilcox.test)
wx_Tr_null <- apply.test(whole_data, "Triples", "null", wilcox.test)

## Applying Bonferroni correction
wx_RF_best[,c(2,4,6)] <- p.adjust(wx_RF_best[,c(2,4,6)], method = "bonferroni")
wx_Tr_best[,c(2,4,6)] <- p.adjust(wx_Tr_best[,c(2,4,6)], method = "bonferroni")
wx_RF_null[,c(2,4,6)] <- p.adjust(wx_RF_null[,c(2,4,6)], method = "bonferroni")
wx_Tr_null[,c(2,4,6)] <- p.adjust(wx_Tr_null[,c(2,4,6)], method = "bonferroni")

## Print the results
wx_RF_best
wx_Tr_best
wx_RF_null
wx_Tr_null
```
